### 2024-02-20 revision/reply_to_reviewer2.tex

Thanks for the careful reading and for your helpful comments and
suggestions.  Please find below point-by-point replies (in black) to
your comments and questions (which are reprinted in blue). To give you
an overview of all the changes in the paper, we also provide a
diff-document that highlights the changes between the initial
submission and this re-submission.\\[1ex]

\referee{I have read the paper with pleasure and have the following
  suggestions for improvement:\\}

\begin{enumerate}
\item \referee{Interesting work, generally well-written. Perhaps a
  small illustrative example with a few figures at the beginning could
  help understand the procedure intuitively.}

  \noindent{
  	Thank you for this suggestion, which we agree can help the reader better understand the intuition behind the method. We added a 2D blurring kernel example, with figures illustrating the end-to-end PSF method. These are shown in the introduction and the numerical results sections (Sections 1 and 7.3).
}

@@

\item \referee{possibly interesting references for estimating Hessians
  in linearised seismic imaging include:
  \url{https://doi.org/10.1016/j.acha.2007.06.007},
  \url{https://doi.org/10.1190/1.2836323}}

  \noindent{We added text in the paragraph at the end of Section 2 to discuss the (lack of) applicability of the method to wave inverse problems and added these references.}

\item \referee{How about comparison with other methods, like those
  proposed in [7],[52]? and you say a bit more? it is hard to conclude
  that your method will always outperform these methods.}

    \noindent{We added a numerical comparison of our method with the HODLR method in [7] for a blur kernel in Table 5 of Section 7.3 in the revised manuscript. The results show that the HODLR method requires hundreds to thousands of operator applies to achieve modest accuracies (e.g., 10\% error) while our method requires only order 10 operator applies. In Section 2 of the revised manuscript we also added a discussion of the costs of the method proposed in [52]. We present back of the envelope calculations based on complexity estimates given in [52], showing that thousands of operator applies may be required.	
%    	For ref 7: Ask Tucker if we could do HODLR on the
%      Hessian coming from ice mountain problem and record the number
%      of mat-vecs needed to achieve a certain accuracy, something like
%      Figure 8 in teh HODLR paper (DONE).
%      
%      Nick will do some estimates to
%      compare things with ref 52.
  }

### 2024-02-20 revision/reply_to_reviewer1.tex

%	NICK ADD PLOT
%	
%	In particular, we note the poor performance for the Ricker wavelet-type kernel (right two columns of Figure 7). We observed a similar configuration for the impulse responses for the Hessian and Gauss-Newton Hessian in wave inverse problems.

%	 The configuration of negative numbers in this example is similar The negative numbers in the integral kernel for the wave Hessian (and Gauss-Newton Hessian) are distributed in a manner similar to the Ricker wavelet-type impulse response shown in the right two columns of Figure 7.
%	
%	 We also added a discussion of the impact of non-locality and negativity on the performance of the method (Section 3.2).
%	
%	The 
%	
%	(1) Three-figure plot: Stokes, Advection/diffusion, wave impulse responses. 
%	
%(2) showing that the method performs poorly for the ricker example
%	
%Nick will try to get an impulse response for the wave
%  problem.
}

\item \referee{It is interesting to see the effectiveness of the
  approximate Hessian used as a preconditioner. It would also be very
  interesting to see how accurate the approximate Hessian is compared
  to a full Hessian in terms of the number of batches, ellipsoid
  sizes, and in particular the total number of impulse responses. Can
  you say anything about the convergence of the approximation, either
  numerical or theoretical?}

  \noindent{
  	In Figure 14 in the revised manuscript we added a convergence study for one of the blur kernel examples. We show the convergence of the proposed PSF method as a function of the total number of impulse responses and the number of batches, for several ellipsoid size parameters $\tau$ ranging from $2.0$--$4.0$. We observe a roughly linear convergence rate until a limit, which depends on $\tau$, is reached. The larger $\tau$ is, the smaller the limit is on the achievable error. Before this limit, the error decreases at roughly the same rate for all $\tau$ in terms of the number of impulse responses. This means that the error decreases faster for smaller $\tau$ as a function of the number of batches, since smaller $\tau$ means more impulse responses per batch. Basically, with larger $\tau$ the method converges more slowly than with smaller $\tau$, but larger $\tau$ allows the method to eventually achieve a lower level of error. We added a discussion of this convergence study in Section 7.3 of the revised manuscript.

### 2024-02-20 revision/reply_to_reviewer2.tex

\begin{enumerate}
\item \referee{Interesting work, generally well-written. Perhaps a
  small illustrative example with a few figures at the beginning could
  help understand the procedure intuitively.}

  \noindent{
  	Thank you for this suggestion, which we agree can help the reader better understand the intuition behind the method. We added a 2D blurring kernel example, with figures illustrating the end-to-end PSF method. These are shown in the introduction and the numerical results sections (Sections 1 and 7.3).
}

\item \referee{possibly interesting references for estimating Hessians
  in linearised seismic imaging include:
  \url{https://doi.org/10.1016/j.acha.2007.06.007},
  \url{https://doi.org/10.1190/1.2836323}}

  \noindent{We added text in the paragraph at the end of Section 2 to discuss the (lack of) applicability of our method to wave inverse problems, and added these references.}
